Changes to police demand in COVID-19 pandemic

### 2022-03-24 docs/index.Rmd
final final final final updates to n8 webinar slides

> "… there are also people calling in because they wanted advice about regulations or were uncertain about what they were allowed to do things …" (interview 3)

@@

> "We have an FAQ. That specially for FCC stuff. And most of the answers can be found in there … There was plenty of support here at work … we had a very large VDU display on the wall with the latest rules and regulations like a like a PowerPoint running through on a continual rotation." (interview 1)

@@

> "I remember a lady who was desperately upset. She was very, very distressed and this must have been as lockdown was easing a bit because her husband had actually gone out and this was the first opportunity she'd had to make the call … that Lady had more than likely gone through all sorts before she could actually found the opportunity to ring it in." (interview 1)

@@

- Expressions of concern
- Calls for advice
- Violence drop
- No change in domestic violence
- For ASB the caller "profile" changed

@@

---
class: center, middle, invesre

>>>>

> "… there are also people calling in because they wanted advice about regulations or were uncertain about what they were allowed to do …" (interview 3)

@@

> "We have an FAQ. That specially for FCC staff. And most of the answers can be found in there … There was plenty of support here at work … we had a very large VDU display on the wall with the latest rules and regulations like a like a PowerPoint running through on a continual rotation." (interview 1)

@@

> "I remember a lady who was desperately upset. She was very, very distressed and this must have been as lockdown was easing a bit because her husband had actually gone out and this was the first opportunity she'd had to make the call … " (interview 1)

@@

- Expressions of concern
- Calls for advice
- Violence drop
- No change in domestic incidents
- For ASB the caller "profile" changed

@@
